---
title: "Combining Subject Data To Master"
author: "Paul A. Bloom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This script pulls from all the raw data files to create a master data spreadsheet
Also, it uses approximate string matching to code correct/incorrect responses in the test phase
It outputs a csv called "behavioral_data.csv

```{r}
# Load Packages -----------------------------------------------------------


library(ggplot2)
library(dplyr)
library(readr)
library("car")

# Import Participant Files ------------------------------------

path = "data-raw/behavioral/"
file.names <- dir(path, pattern =".csv")
file.names
master <- data.frame()


# Make the master data frame -- the loop matches up the initial [SUB#].csv file for each subject during the TOT phase 
# with the test[SUB#].csv file from the test phase, then appends them all into a master file. 
#Subject 1 was previously excluded -- not included here

for(i in 2:30) {
  subject_frame <- read.csv(paste(path, file.names[i], sep = ''), stringsAsFactors=FALSE)
  test_frame <- read.csv(paste(path, file.names[i+30], sep = ''), stringsAsFactors=FALSE, col.names = 
                           c("test_id", "test_trialnum", "question_num", "test_question", "subj_answer", "correct_answer"))
  subject_comp <- merge(subject_frame,test_frame,by="question_num")
  master <- rbind(master, subject_comp)
}


# Approximate String Matching For Typed Responses ---------------------------------------------

# Make a new column called "recall" in the data frame and loop through each trial, coding each as correct or 
# not correct in the test phase via approx pattern matching

master$recall <- rep(0, length(master$question_num))
for(i in 1:length(master$recall)){
  matcher<- agrep(master$correct_answer[i], master$subj_answer[i], ignore.case = T, value = F,
        max.distance = 0.1)
  if(length(matcher) != 0)
  {
    master$recall[i] <- "C"
  }
  else{
    master$recall[i] <- "I"
  }
  
}

# Save raw behavioral master file
save(master, file = "data-raw/behavioral_data_raw.rda")

```

In between here, manual data cleaning and entry of trials in which the experimenter hit the wrong key happens. These trials where the experimenter hit a wrong key are the trials in the 'mistake' column coded as 1

Now, read in cleaned master, and put it in data folder for use in the package
```{r}
totBehavMasterCleaned <- read.csv('data-raw/behavioral_data_cleaned.csv', stringsAsFactors = F)
devtools::use_data(totBehavMasterCleaned, compress = 'xz')
```

This behavioral_data.csv file is then checked and recall is corrected by an experimenter blind to the tot coding for each trial

Mostly, responses coded as incorrect because of spelling errors or additional words are recoded as correct by the experimenter
