---
title: "Behavioral Analysis"
author: "Paul A Bloom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette

vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Behavioral Analysis Script

This script takes the cleaned master file, excludes a few subjects, then gets basic descriptive stats and computes behavioral analyses


```{r}
# Load Packages -----------------------------------------------------------
library(ggplot2)
library(tidyverse)
library(readr)
library("car")

# Use data from package
library(totERP)
str(totBehavMasterCleaned)
```

Exclude subjects with <5 usable ERP Trials (this criterion came from checking ERP data) for both TOT and no-TOT conditions
```{r}
# Remove Subjects Based on <5 Usable Trials in ERP Data
totBehavMasterCleaned <- subset(totBehavMasterCleaned, id !=2)
totBehavMasterCleaned <- subset(totBehavMasterCleaned, id !=5)
totBehavMasterCleaned <- subset(totBehavMasterCleaned, id !=19)
head(totBehavMasterCleaned)
```

# Clean master of experimenter mistakes and code for descriptives

```{r}
totBehavMasterCleaned <- subset(totBehavMasterCleaned, mistake == 0)
totBehavMasterCleaned$acc[totBehavMasterCleaned$recall == "C"] <- 1 #1 for correct
totBehavMasterCleaned$acc[totBehavMasterCleaned$recall == "I"] <- 0 #2 for incorrect
totBehavMasterCleaned$tot_cond[totBehavMasterCleaned$tot == "yes"] <- 1
totBehavMasterCleaned$tot_cond[totBehavMasterCleaned$tot == "no"] <- 0
totBehavMasterCleaned$tot_cond[totBehavMasterCleaned$tot == "N/A"] <- 0
totBehavMasterCleaned$ans_cond[totBehavMasterCleaned$tot == "yes"] <- 0
totBehavMasterCleaned$ans_cond[totBehavMasterCleaned$tot == "no"] <- 0
totBehavMasterCleaned$ans_cond[totBehavMasterCleaned$tot == "N/A"] <- 1
totBehavMasterCleaned$dk_cond[totBehavMasterCleaned$tot == "yes"] <- 0
totBehavMasterCleaned$dk_cond[totBehavMasterCleaned$tot == "no"] <- 1
totBehavMasterCleaned$dk_cond[totBehavMasterCleaned$tot == "N/A"] <- 0

```

# Get the average proportion of questions eliciting TOT, 'Don't Know', and answer responses
```{r}

# Average Proportion of TOTs

totsbysubject <- totBehavMasterCleaned %>%
  group_by(id) %>% summarise(n = n(), totnum = sum(tot_cond), totprob = totnum/n,
                             ansnum = sum(ans_cond), ansprob = ansnum/n,
                             dknum = sum(dk_cond), dkprob = dknum/n)

#probability of getting tot
mean(totsbysubject$totprob)
sd(totsbysubject$totprob)

# probability of getting answer
mean(totsbysubject$ansprob)
sd(totsbysubject$ansprob)

# probability of 'don't know'
mean(totsbysubject$dkprob)
sd(totsbysubject$dkprob)



# Check to make sure the means add up to 1
mean(totsbysubject$totprob) + mean(totsbysubject$ansprob) + mean(totsbysubject$dkprob)

```

Now, filter out trials where subjects answered
```{r}
totBehavMasterCleaned <-filter(totBehavMasterCleaned, tot != "N/A") # Take Out Trials Where Subject Answered

```

# How Many TOTs Did Each Subject Have?
```{r}

totBehavMasterCleaned$tot <- as.factor(totBehavMasterCleaned$tot)

e <- totBehavMasterCleaned %>% 
  group_by(id, tot) %>%
  summarise(n = n(), recallnum = sum(acc), prob = recallnum/n)
head(e)



group_TOT_Plot <- ggplot(e, aes(x = tot, y = prob)) + 
  stat_summary(fun.data = mean_cl_boot) + 
  geom_jitter(size = .5, width = .02, col = 'blue')
group_TOT_Plot + 
  labs(x = "TOT State - points are individual subject probabilities", 
       y = "P(Recall)", 
       title = "Recall Probability by TOT")

# T Test


t.test(e$prob ~ e$tot, paired = T)


```
# Some Summary Stats

```{r}
mean(e$prob[e$tot == "yes"]) #.751 average recall following tot states
mean(e$prob[e$tot == "no"]) #.516 average recall following don't know
mean(e$prob[e$tot == "yes"]) - mean(e$prob[e$tot == "no"]) #23.5% difference
sd(e$prob[e$tot == "yes"]) #.115 sd for tot state recall
sd(e$prob[e$tot == "no"]) #.187 sd for don't know recall


# Other Summary Statistics -------------------------------------------

# Some descriptives on how many TOTs each subject experienced

head(totsbysubject)
summary(totsbysubject$totnum)
mean(totsbysubject$totnum)/150 #on average 21% of trials elicited TOTs
sd((totsbysubject$totnum)/150) #Standard deviation for proportion of trials eliciting TOTs (.085)

#How was recall in general?
totBehavMasterCleanedrecall <- totBehavMasterCleaned %>% 
  group_by(id) %>% summarise(n = n(), recallnum = sum(acc), recallprop = recallnum/n)

head(totBehavMasterCleanedrecall)
mean(totBehavMasterCleanedrecall$recallprop) #.59 mean recall rate overall
sd(totBehavMasterCleanedrecall$recallprop) #.16 sd for recall rate

```

Within-Subjects Scatter Plot of Recall Probability (Conditional on TOT/no-TOT)

```{r}
e1 <- select(e, id, tot, prob)
subject_means_wide <-
  spread(e1,
         key = tot,
         value = prob,
         sep = "_")
head(subject_means_wide)

withinSubScatter <- ggplot(subject_means_wide, aes(x = tot_no, y = tot_yes)) +
  geom_point() +
  xlim(0,1) +
  ylim(0,1) +
  geom_abline() + 
  theme_bw() + 
  theme(aspect.ratio=1) +
  labs(x = 'P(Recall | No-TOT)', y = 'P(Recall | TOT)')
withinSubScatter
```
